Tutorial_2b

### 2024-10-19 Tutorial_2b.Rmd
update tutorials 2a and 2b

```{r}
model_M4_ca <- readRDS("Tutorial_2_Bayesian/models/model_M4_ca.rds")
```

@@

# plot effects on hazard ratio scale

```{r haz-ratio}
plot_facet_hr <- post %>% 
  mutate(Congruent = b_conditioncongruent + period_9 * `b_conditioncongruent:period_9` + period_9sq * `b_conditioncongruent:Iperiod_9E2` + period_9cu * `b_conditioncongruent:Iperiod_9E3`,
         Incongruent = b_conditionincongruent + period_9 * `b_conditionincongruent:period_9` + period_9sq * `b_conditionincongruent:Iperiod_9E2` + period_9cu * `b_conditionincongruent:Iperiod_9E3`) %>%

@@

```{r subject-hazard}
make_fitted(model_M4_ca, scale = "response") %>% 
  mutate(cond   = rep(rep(c("N","C","I"),each=30),6),
         trial  = factor(trial_c,levels=c(-0.5,0.0,0.5),labels=c("trial 500","trial 1000","trial 1500")),
         period = period_9+9) %>% 
  filter(pid==selected_subject) %>% 
  # plot
  ggplot(aes(x = period, y = Estimate, ymin = Q2.5, ymax = Q97.5,
             fill = condition, color = condition)) +
  geom_ribbon(alpha = 1/5, linewidth = 0) +
  geom_line() +
  scale_fill_viridis_d(NULL, option = "A", end = .6, direction = -1) +
  scale_color_viridis_d(NULL, option = "A", end = .6, direction = -1) +
  scale_x_continuous("time bin endpoint", breaks = 6:15, limits = c(6, 15), labels=c(6:15)*40) +
  ylab("fitted ca(t)") +
  coord_cartesian(ylim = c(0, 1)) +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill="white",color="black"),
        legend.position = "top",
        axis.text.x = element_text(angle=90)) +
  facet_wrap(~ trial)
```

>>>>

```{r load-model-M4-ca}
model_M4_ca <- readRDS("Tutorial_2_Bayesian/models/model_M4_ca.rds")
```

@@

# plot effects on odds ratio scale

```{r odds-ratio}
plot_facet_hr <- post %>% 
  mutate(Congruent = b_conditioncongruent + period_9 * `b_conditioncongruent:period_9` + period_9sq * `b_conditioncongruent:Iperiod_9E2` + period_9cu * `b_conditioncongruent:Iperiod_9E3`,
         Incongruent = b_conditionincongruent + period_9 * `b_conditionincongruent:period_9` + period_9sq * `b_conditionincongruent:Iperiod_9E2` + period_9cu * `b_conditionincongruent:Iperiod_9E3`) %>%

@@

```{r subject-ca}
make_fitted(model_M4_ca, scale = "response") %>% 
  mutate(cond   = rep(rep(c("N","C","I"),each=30),6),
         trial  = factor(trial_c,levels=c(-0.5,0.0,0.5),labels=c("trial 500","trial 1000","trial 1500")),
         period = period_9+9) %>% 
  filter(pid==selected_subject) %>% 
  # plot
  ggplot(aes(x = period, y = Estimate, ymin = Q2.5, ymax = Q97.5,
             fill = condition, color = condition)) +
  geom_ribbon(alpha = 1/5, linewidth = 0) +
  geom_line() +
  scale_fill_viridis_d(NULL, option = "A", end = .6, direction = -1) +
  scale_color_viridis_d(NULL, option = "A", end = .6, direction = -1) +
  scale_x_continuous("time bin endpoint", breaks = 6:15, limits = c(6, 15), labels=c(6:15)*40) +
  ylab("fitted ca(t)") +
  coord_cartesian(ylim = c(0, 1)) +
  theme(panel.grid = element_blank(),
        panel.background = element_rect(fill="white",color="black"),
        legend.position = "top",
        axis.text.x = element_text(angle=90)) +
  facet_wrap(~ trial)
```
